%!TEX program = xelatex
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font

\setlength{\textwidth}{5.1in}
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont{Heiti SC} 
\XeTeXlinebreaklocale “zh”
\XeTeXlinebreakskip = 0pt plus 1pt minus 0.1pt % Break line

\newfontfamily{\H}{Songti SC} % Chinese font

\begin{document}

%	NAME AND ADDRESS SECTION

\moveleft.5\hoffset\centerline{\large\bf 测试} % name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{测试} % address
\moveleft.5\hoffset\centerline{City, State 12345}
\moveleft.5\hoffset\centerline{(000) 111-1111 or (111) 111-1112}

\begin{resume}

%	OBJECTIVE SECTION
 
\section{职位}  

测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试测试

%	EDUCATION SECTION

\section{EDUCATION}

{\sl Bachelor of Science,} Interdisciplinary Science \\
Rensselaer Polytechnic Institute, Troy, NY, expected December 1990 \\
Concentration: Computer Science \\
Minor: Management 
 
%	COMPUTER SKILLS SECTION

\section{COMPUTER \\ SKILLS} 

{\sl Languages \& Software:} 
COBOL, IFPS, Focus, Megacalc, Pascal, Modula2, C, APL, SNOBOL, FORTRAN, LISP, SPIRES, BASIC, VSPC Autotab, IBM 370 Assembler, Lotus 1-2-3. \\
{\sl Operating Systems:} MTS, TSO, Unix. 
 
%	PROFESSIONAL EXPERIENCE SECTION
 
\section{EXPERIENCE}

{\sl Business Applications Programmer} \hfill Fall 1990 \\
Allied-Signal Bendix Friction Materials Division, Financial Planning Department, Latham, NY 

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed four ``user friendly" forecasting systems each of which produces 18 to 139 individual reports. 
\item Developed or improved almost all IFPS programs used for financial reports. 
\end{itemize}
 
{\sl Research Programmer} \hfill Summer 1990 \\
Psychology Department, Rensselaer Polytechnic Institute 
\begin{itemize} 
\item Performed computer aided statistical analysis of data. 
\end{itemize} 

{\sl Assistant Manager} \hfill Summers 1988-89 \\
Thunder Restaurant, Canton, CT
\begin{itemize}
\item Recognized need for, developed, and wrote employee training manual. Performed various duties including cooking, employee training, ordering, and inventory control. 
\end{itemize} 

%	COMMUNITY SERVICE SECTION

\section{COMMUNITY \\ SERVICE}

Organized and directed the 1988 and 1989 Grand Marshall Week \\
``Basketball Marathon.'' A 24 hour charity event to benefit the Troy Boys Club. Over 250 people participated each year. 

%	EXTRA-CURRICULAR ACTIVITIES SECTION

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

Elected {\it House Manager}, Rho Phi Sorority \\
Elected {\it Sports Chairman} \\
Attended Krannet Leadership Conference \\
Headed delegation to Rho Phi Congress \\
Junior varsity basketball team \\
Participant, seven intramural athletic teams 

\end{resume}
\end{document}
